**Density Dependence**

### 2022-12-15 Rmd/runCond.Rmd
added dropbox dir

---
title: "**Density Dependence**"
subtitle: "Summary"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
mathjax: TRUE

@@

theme_set(theme_bw(16))
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "dd"))

@@

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel("../data/inputs/dat.xlsx",3))

>>>>

---
title: "**Density Dependence**"
subtitle: "Summary"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

theme_set(theme_bw(16))

source("../R/get_dropbox.R")

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

@@

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel(file.path(dropboxdir,"data/inputs/dat.xlsx"),3))
